Probabilistic Catalogs for Crowded Stellar Fields

### 2012-11-08 paper/ms.tex
acks

\section{Acknowledgements}
It is a pleasure to thank Phil Marshall, Dustin Lang, and Geraint Lewis for
their comments on earlier versions of this work. BJB would also like to thank
Wayne Stewart and Arden Miller for their support during his first semester at
Auckland.

>>>>

\section{Acknowledgements}
It is a pleasure to thank
  Jonathan Goodman (NYU),
  Fengji Hou (NYU),
  Dustin Lang (CMU),
  Geraint Lewis (Sydney), and
  Phil Marshall (Oxford)
for their comments and discussions.
BJB would also
like to thank Wayne Stewart and Arden Miller for their support during
his first semester at Auckland.
DFM and DWH were partially supported by
   the US National Science Foundation (grant IIS-1124794) and
   the US National Aeronautics and Space Administration (grant NNX12AI50G).
